\begin{document}
Preclinical research is key for the advancement of life sciences. The use of experimental animal models in the basic health sciences historically helped the humanity to find pathological mechanisms of diseases as well has promoted the development of therapeutic strategies, medicines and vaccines. It is paramount that experiments conducted on preclinical research be reproducible. Sharing experimental data between different institutions and cooperative researchers worldwide may accelerate science and technology innovation in the health sciences, however a large number of experiments are not reproducible. Factors leading to irreproducible research on preclinical studies fall into four major categories: Biological reagents and reference materials,  study design, data analysis and reporting and laboratory protocols. The data analysis and reporting category concentrates 25.5\% of the total factors, is estimated that \$7.19 billions of the annual research budget, in the US alone, is funding irreproducible experiments. Preclinical research activities generates a vast amount of data and scientists ought to collect and share it properly, on the other side the scientific community needs to easily get access to data from open, verifiable and reliable sources in order to reproduce and validate experiments. 
Technologies based on concepts such as peer-to-peer networks, hashes, smart contracts, distributed digital ledgers and distributed files systems can be integrated to build a decentralised application (DApp) that can provide services to store, safeguard, track changes and distribute data from experiments.  
Applying a computational strategy in the sharing of data between researchers might help science development, also improving animal research. This paper explores the use of the universal principles of DApps to improve the reproducibility of preclinical experiments.

\keywords{blockchain, distributed ledger, data analysis, decentralised technology, experiments irreproducibility, experiments reproducibility, DApps, DStorage, IPFS, smart contracts.}

\end{document}